\documentclass[oneside,12pt]{memoir}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.markings}

\hypersetup{colorlinks=true,urlcolor=blue}

\newcommand{\bb}{\mathbb}
\newcommand{\mc}{\mathcal}
\newcommand{\ms}{\mathscr}

\makeoddhead{myheadings}{Math 381}{Discrete Mathematical Modeling}{\thepage}
\pagestyle{myheadings}

\setlist[enumerate,2]{label = (\alph*)}

\begin{document}

\begin{center}
\textbf{\large Homework 2} \\
\emph{Due Tuesday, January 12}
\end{center}

These problems are from \emph{Operations Research, Fourth Edition} by Wayne Winston. See the syllabus or click \href{https://ia801301.us.archive.org/16/items/OperationalResearchWinstonWayne/Operational-Research-Winston-Wayne.pdf}{here} for a link to the pdf.

For each linear program, please state
\begin{itemize}
	\item what the variables are
	\item what the objective function is
	\item what each constraint comes from
\end{itemize}

For Problem 4 you will need to use an LP solver. I recommend using \href{https://developers.google.com/optimization}{OR-Tools}, a free software suite developed by Google. It can be used with Python, Java, C++, and C\#. Installation instructions can be found in the previous link or \href{https://developers.google.com/optimization/install}{here}, and detailed instructions on how to use it to solve linear programs can be found \href{https://developers.google.com/optimization/lp/lp_example}{here}. If you are having trouble, please post a question on the Ed Discussion board or come to office hours.

MATLAB can also solve linear programs. See \href{https://www.mathworks.com/help/optim/linear-programming-and-mixed-integer-linear-programming.html?s_tid=CRUX_lftnav}{here}. Note that I don't have experience with MATLAB, so I won't be able to help if you have problems. You can try the Ed Discussion board if you have a question.

Finally, please write your linear program for Problem 4 separately from the code, using the guidelines above. Once you do this, you do not have to include your code in your submission. It  is enough to write something like ``For this LP, GLOP returned an optimal solution of \dots''. However, if your answer is wrong, submitting the code might help us identify where things went wrong.

\begin{enumerate}[leftmargin=*]

\item Winston, Problem 1, page 113. Solve by hand.
\item Winston, Problem 13, page 115. Do not solve the LP.
\item Winston, Problem 14, page 115. Do not solve the LP.
\item Winston, Problem 46, page 120. Please have the computer solve over the \textbf{real numbers}, not the integers. You will not get credit if you use an integer program solver. After you solve the LP, you may need to do some additional work to make a realistic recommendation. You do not have to prove that your recommendation is the best possible.

\end{enumerate}

\end{document}