\documentclass[oneside,12pt]{memoir}

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.markings}

\newcommand{\bb}{\mathbb}
\newcommand{\mc}{\mathcal}
\newcommand{\ms}{\mathscr}

\makeoddhead{myheadings}{Math 381}{Discrete Mathematical Modeling}{\thepage}
\pagestyle{myheadings}

\setlist[enumerate,2]{label = (\alph*)}

\begin{document}

\begin{center}
\textbf{\large Homework 1} \\
\emph{Due Tuesday, January 9}
\end{center}

The purpose of this assignment is to make sure you have the prerequisite knowledge of linear algebra. You may find it helpful to read Sections 2.1--2.3 of Winston as a review.

Solutions may be hand-written or typed. Please submit through Gradescope.

\begin{enumerate}[leftmargin=*]

\item Find all solutions, by hand, to the system of equations
\begin{align*}
x + y + z &= 3 \\
x + 2y &= 2 \\
y - z &= -1
\end{align*}
Show all your work.

\item During any given year, 10\% of all rural residents move to the city, and 20\% of all city residents move to a rural area (all other people stay put). Let $R_t$ be the number of rural residents at the beginning of year $t$, and $C_t$ be the number of city residents at the beginning of year $t$. Use matrix multiplication to relate the vector $\begin{pmatrix}
R_{t+1} \\ C_{t+1} \end{pmatrix}$ to the vector $\begin{pmatrix}
R_{t} \\ C_{t} \end{pmatrix}$.

\item Consider the real system of equations $Ax = b$, where $A$ is an $n \times n$ matrix, and $x$ and $b$ are column vectors with $n$ entries. Suppose that the entries of $A$ and $b$ are found by measurement, and this measurement has a small, random error which is independent for all the entries. Do you expect the system $Ax = b$ to have zero, one, or infinitely many solutions? Explain your reasoning. You do not need to give a rigorous proof, but you should give some convincing reasoning.

\end{enumerate}

\end{document}